Industrial Best Practice

### 2015-03-22 ibp/ibp.tex
v1 dissemniationp lan

\section{Dissemination Plan, 2p}

\begin{itemize}
	\item Description on how to present/sell the solution to the company
	\item Description on how to communicate the solution
\end{itemize}

Research findings and products—What is going to be disseminated?

II.
End users—Who will apply it in practice?

III.
Dissemination partners—Individuals, organisations or networks through whom you can reach end users?

IV.
Communication—How you convey the research outcomes?

V.
Evaluation—How you determine what worked?

VI.
Dissemination work plan—Where you start?
\newpage

@@

\subsection{Impact on Technology and State of the Art}
The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem in the assessment when creating APIs. This would lead to a more homogeneous environment where API platforms and API users can change their code jointly, to reduce the risk of deprecating for example methods. The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems. Probable areas where this could have an especially great impact would be in the areas of web development APIs, since they are widely used by a great amount of users. Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist. The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.

>>>>

\section{Dissemination Plan, 2p}
This section will describe the dissemination plan for our framework.

\subsection{End-users}

Two major end-users of our framework have been identified, 1) open-source projects and 2) web development APIs. The reason open-source projects have been identified as potential users of our API is that they generally have a good-will mindset when it comes to developing the software engineering industry. Their goals are not set on making profit, but delivering a product that is as good as possible. The open-source community also takes care of itself and thus it cares about the well-being of its ecosystems. The second area where this could have an especially great impact would be in the area of web development APIs, since they are widely used by a great amount of users. Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist. The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.

\subsection{Presentation and Communication}
The main way of conveying our message would be through the research community. The initial studies that will be conducted (as mentioned in Section 3) will lead to a number of published research papers. These will be used to create awareness and attention of our framework. The papers may also lead to other researchers building on our research which would only help our cause which is to improve APIs everywhere.

In addition to reaching out to the research community, conferences related to web development would be targeted especially. One example of such a conference is JDays, where many APIs that are developed in JavaScript are discussed. The main reason for targeting such conferences is that a large part of the important persons of the community attend. This would help to create further awereness and publicity.

The last way of presenting our framework would be through directly targeting a set of companies that operate in the same software ecosystem. One example of that would be to target a company which develops a game engine, and at the same time contact the most prominent game developers which utilise this game engine. If the company developing the game engine realises that there is large interest from the main users of their API, it is much more likely that they would be interested in using our API.

@@

\subsection{Impact on Technology and State of the Art}
The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem in the assessment when creating APIs. This would lead to a more homogeneous environment where API platforms and API users can change their code jointly, to reduce the risk of deprecating for example methods. The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems.
